Hadoop Image Processing Framework

### 2015-03-15 Paper.tex
Finished editing, except for related work.

\end{lstlisting}
\section{Conclusion}
This paper has described our framework fo image processing for large scale image processing applications on the MapReduce framework. The framework is designed to abstract the technical details of Hadoop's powerful MapReduce framework and provide a way for users who want to process large image datasets. We provided a how the images can be stored in different hadoop file format and efficient access within Map Reduce pipeline and simple modules to make the framework more easier. By providing interoperability between different image data types we give the user to process the images using different open-source image processing libraries. Finally, we provide a way to overcome the loss of image headers after processing which are most useful for image processing and vision applications.

With these features, the framework brings a new level of transparency and simplicity for creating large-scale image processing applications over Hadoop's MapReduce framework. The paper describes to example applications built using the framework to demonstrate the power of the framework. We hope that this level of abstractness to use Hadoop MapReduce framework will enhance the ability to create large-scale image processing applications with ease.

\section{Future Work}
In the near future we hope to extend the framework into a full-fledged multimedia processing framework. We would like to improve framework such that audio and video processing over hadoop is done with ease. We also intend to add a CUDA module for using the graphics card for processing the images. Finally, we intend to wrap our system into an highly parallelized open-source hadoop multimedia processing framework and perhaps provide a sample web-based graphic user interface with all image processing applications.

>>>>

\end{lstlisting}
\section{Conclusion}
This paper has described our Hadoop Image Processing Framework for
implementing large scale image processing applications.  The framework
is designed to abstract the technical details of Hadoop's powerful
MapReduce system and provide an easy mechanism for users to process
large image datasets. We provide software machinery for storing images
in the various Hadoop file formats and efficiently accessing the Map
Reduce pipeline.  By providing interoperability between different
image data types we allow the user to leverage many different
open-source image processing libraries. Finally, we provide the means
to preserve image headers throughout image manipulation process,
retaining useful and valuable information for image processing and
vision applications.

With these features, the framework provides a new level of
transparency and simplicity for creating large-scale image processing
applications on top of Hadoop's MapReduce framework.  We demonstrate
the power and effectiveness of the framework in terms of performance
enhancement and complexity reduction.  The Hadoop Image Processing
Framework should greatly expand the population of software developers
and researchers easily able to create large-scale image processing
applications.

\section{Future Work}
In the near future we hope to extend the framework into a full-fledged
multimedia processing framework. We would like to improve the
framework to handle audio and video processing over Hadoop with
similar ease. We also intend to add a CUDA module to allow processing
tasks to make use of machines' graphics cards. Finally, we intend to
develop our system into a highly parallelized open-source Hadoop
multimedia processing framework, providing web-based graphical user
interfaces for image processing applications.
